### 2020-05-13 v0.1.4/assets/TaskForComponents/components.tex
build based on 76fe946

\tikzset{
    clockborder/.style = { 
        trapezium, trapezium angle=60, minimum width=1cm, draw, very thick
    },
    Clock/.pic = {
        \node [clockborder, shape border rotate=-180](-clockedge){#1};
        \draw[very thick] (-clockedge.east) -- ++(2cm, 0cm);
        \def\sft{0.5}
        \foreach \x in {0, 0.5, 1, 1.5}{
            \draw[very thick] (\x + \sft, 0.1) -| ++(0.25cm, 0.25cm) -| ++ (0.25cm, -0.25cm);
        }
    },
}

\begin{document}
    \begin{tikzpicture}[every node/.style={font=\normalsize}]
        % Place the blocks 
        \draw(-3.5, 0) pic (gen) {Component={Sinewave\\Generator}{t}};
        \draw pic (adder) {Component={Adder}{t}};
        \draw(3.5, 0) pic (ds) {Component={ODESystem}{t}};
        \draw(7, 1.5) pic (writer) {Component={Writer}{t}};
        \draw(2, -2.25) pic (memory) {Component={Memory}{t}};
        % Glow the blocks
        % \drawshadowbis{gen-edge};
        % \drawshadowbis{adder-edge};
        % \drawshadowbis{ds-edge};
        % \drawshadowbis{writer-edge};
        % \drawshadowbis{memory-edge};
        \begin{scope}[line width=1.5mm, ->, >={Triangle[width=3mm,length=3mm]}]
            \draw[-] ([yshift=2mm] gen-edge.east) -- ++(1cm, 0cm) node[midway, anchor=south]{$r(t)$} coordinate(d); 
            \draw (d) -- ([yshift=2mm]  adder-edge.west);
            \draw (adder-edge.east) -- node[midway, anchor=south]{$u(t)$} (ds-edge.west);
            \draw[-] (ds-edge.east) -- ++(1cm, 0cm) node[midway, anchor=south]{$y(t)$} coordinate (a);
            \draw (a) |- ([yshift=-3mm] writer-edge.west);
            \draw (a) |- (memory-edge.east);
            \draw[-] (memory-edge.west) -- ++(-2.5cm, 0cm) coordinate (c);
            \draw ([yshift=-0.75mm] c) |- ([yshift=-2mm] adder-edge.west);
            \draw (d) |- ([yshift=3mm] writer-edge.west);
        \end{scope}
        \draw[very thick, dashed] (-5, 3) rectangle (8.5, -4);
        \node at (7.5, -3.5) {Model};

         % \Place clock 
        \begin{scope}[shift={(-4.25cm, -3.25cm)}]
            \draw pic(clk) {Clock={T}} ;
        \end{scope}

    \end{tikzpicture}
\end{document}

>>>>

\begin{document}
    \begin{tikzpicture}
        % Place the blocks 
        \draw pic (b1) {Component={B1}{t}};
        \draw(3.5, 0) pic (b2) {Component={B2}{t}};
        % % Glow the blocks
        % \drawshadowbis{b1-edge};
        % \drawshadowbis{b2-edge};
        \begin{scope}[line width=1.5mm, >={Triangle[width=3mm,length=3mm]}]
            \draw[->] ([xshift=-1cm] b1-edge.west) -- node[midway, anchor=south]{L1} (b1-edge.west);
            \draw[->] (b1-edge.east) -- node[midway, anchor=south]{L2} (b2-edge.west);
            \draw[->] (b2-edge.east) -- node[midway, anchor=south]{L3} ([xshift=1cm] b2-edge.east);
        \end{scope}
    \end{tikzpicture}
\end{document}

### 2020-05-13 v0.1.4/assets/Tasks/reader_writer_task.tex
build based on 76fe946

\tikzset{
    border/.style = { 
        draw, circle, minimum width=2cm, ultra thick
    },
    pics/Task/.style={
        code = {
            \node [border, align=center](-edge){#1};
    }}
    }

\begin{document}
    \begin{tikzpicture}[every node/.style={font=\Large}]
        \draw (0, 0) pic (t1) {Task={B1}};
        \draw (2.5, 0) pic (t2) {Task={B1}};
        \draw (6.5, 0) pic (t3) {Task={B2}};
        \draw (9,0) pic (t4) {Task={B2}};
        \begin{scope}[line width = \lw, >={Triangle[width=4mm,length=4mm]}, ->]
            \draw ([xshift=-1.25cm] t1-edge.west) -- node[midway, anchor=south]{L1} (t1-edge.west);
            \draw (t2-edge.east) -- node[midway, anchor=south]{L2}  (t3-edge.west);
            \draw[line width = \lw, ->] (t4-edge.east) -- node[midway, anchor=south]{L3} ([xshift=1cm] t4-edge.east);
        \end{scope}
    \end{tikzpicture}
\end{document}

>>>>

\tikzset{
    border/.style = { 
        draw, circle, minimum width=1cm, thick
    },
    pics/Task/.style={
        code = {
            \node [border, align=center](-edge){#1};
    }}
    }

\begin{document}
    \begin{tikzpicture}
        \draw pic (t1) {Task={Writer\\Task}};
        \draw (3,0) pic (t2) {Task={Reader\\Task}};
        \draw[line width = \lw, >={Triangle[width=4mm,length=4mm]}, ->] (t1-edge.east) -- (t2-edge.west);
    \end{tikzpicture}
\end{document}
